Measuring security performance in the Android ecosystem

### 2015-06-04 ccs.tex
Talk about standard deviation

@@

\section{Comparison with other data}
Here we show that the \da\ data~\cite{Wagner2013} is representative for our purposes by comparing it with two other sources of data which provide an upper and lower bound on it.
The \da\ data is collected from devices across the world where users have voluntarily installed the app.
We have obtained comparable data on 5\,290 devices from a multinational FTSE 100 company's mobile device management database which includes company and employee owned devices, and from 5\,170\,000 matching User-Agent headers on all HTTP traffic for 30\% of Rwanda for a week.
\todo{citation for Rwanda dataset}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/dists}
\caption{Comparison between FTSE, User-Agent and the corresponding \da\ data, error bars indicate 95\% confidence intervals.}
\label{fig:dists}
\end{figure}
We used the data from the FTSE 100 company for the week ending 2015-04-27 and the User-Agent data was collected between 2015-01-31 and 2015-02-12.
Figure~\ref{fig:dists} shows the proportion of devices running each Android OS version in the two comparison data sets and the comparable periods from \da.
The general pattern this shows is that in the FTSE data newer versions are more popular than in the \da\ data and that in the Rwanda data old versions are more popular than in the \da\ data.
\todo{Can we quantify this?}
This shows that \da\ lies between these two biased samples while being similar to both and so is representative.

>>>>

We indicate the uncertainty in our results by presenting them $\pm$ one standard deviation and give results to 3~s.f., this occasionally results in `$\pm\, 0$' when the standard deviation is small.
\todolater{Do we want to use the 95 percentile instead}
We explore systematic errors in \S\ref{sec:representative}.

@@

\section{Comparison with other data}\label{sec:representative}
Here we show that the \da\ data~\cite{Wagner2013} is representative for our purposes by comparing it with two other sources of data which provide an upper and lower bound on it.
The \da\ data is collected from devices across the world where users have voluntarily installed the app.
We have obtained comparable data on 5\,290 devices from a multinational FTSE 100 company's mobile device management database which includes company and employee owned devices, and from 5\,170\,000 matching User-Agent headers on all HTTP traffic for 30\% of Rwanda for a week.
\todo{citation for Rwanda dataset}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/dists}
\caption{Comparison between FTSE, User-Agent and the corresponding \da\ data, error bars indicate 95\% confidence intervals.}
\label{fig:dists}
\end{figure}
We used the data from the FTSE 100 company for the week ending 2015-04-27 and the User-Agent data was collected between 2015-01-31 and 2015-02-12.
Figure~\ref{fig:dists} shows the proportion of devices running each Android OS version in the two comparison data sets and the comparable periods from \da.
The general pattern this shows is that in the FTSE data newer versions are more popular than in the \da\ data and that in the Rwanda data old versions are more popular than in the \da\ data.
\todo{Can we quantify this?}
This shows that \da\ lies between these two biased samples while being similar to both and so is representative.
